---
title: "Stratified Random Sampling Simulation and Parameter Estimation"
author: "Maggie"
output: 
  pdf_document:
    latex_engine: xelatex
---

This report presents a simulation study on the performance of different estimators in stratified random sampling under the influence of outliers, including the Neyman Sample Mean Estimator, the Wang-Xu Hybrid Estimator, and the Proposed Hybrid Estimator. The study evaluates bias, variance, and mean squared error (MSE) across multiple scenarios with varying levels of outliers and different numbers of strata to determine the most robust estimation method.

**Simulation Design\
**A finite population consisting of $100,000$ units was generated and divided into $H$ strata. The data within each stratum was drawn from a normal distribution $N(\mu_h, \sigma^2_h)$, where $\mu_h$ and $\sigma^2_h$ varied across strata to simulate heterogeneity. A fixed proportion of each stratum was replaced with extreme values (outliers) generated from a heavy-tailed $t\mathbb-distribution$ with $1$ degree of freedom , shifted by the mean of the respective stratum. Outliers were introduced randomly across all strata to assess their impact on estimation.

Data was simulated with **5% and 10% outliers** and across **3, 5, and 8 strata**, resulting in six different simulation cases based on the proportion of outliers and the number of strata. Each case was simulated **100 times** to generate a sufficient number of sample statistics for each estimator. The study aimed to compute the **Mean Squared Error (MSE), Bias, and Variance** for each case, allowing a comparison of the following estimators under the influence of outliers and evaluating how stratum sizes affect their estimates.

-   Neyman Sample Mean Estimator: $\hat{Y} = \sum_{h=1}^{H} P_h\bar{y_h}$

-   Wang Xu Hybrid Estimator: $\hat{Y}_{trimmed} = \sum_{h=1}^{H} P_h\left[w\bar{y} + (1-w)T_h\right]$

-   Proposed Hybrid Estimator: $\hat{Y}_{weighted} = \sum_{h=1}^{H} P_h\left[w\bar{y} + (1-w)W_h\right]$

| **Sampling cases:**
| Case 1: Outliers proportion = $5\%$ Number of strata = $3$ Number of simulations = $100$
| Case 2: Outliers proportion = $5\%$ Number of strata = $5$ Number of simulations = $100$
| Case 3: Outliers proportion = $5\%$ Number of strata = $8$ Number of simulations = $100$
| Case 4: Outliers proportion = $10\%$ Number of strata = $3$ Number of simulations = $100$
| Case 5: Outliers proportion = $10\%$ Number of strata = $5$ Number of simulations = $100$
| Case 6: Outliers proportion = $10\%$ Number of strata = $8$ Number of simulations = $100$

Below is a tabular representation of five out of the **100** simulations for each case. The naming convention follows the pattern: **Case-1-2**, where **Case-1** refers to the first case, and **2** indicates the second simulation within that case.

```{r echo= FALSE, warning=FALSE}
stratified_simulation = function(n_strata,
                                 key_parameters,
                                 inject_propotion = 0.1,
                                 t_df = 1,
                                 sample_size = 50000,
                                 sample_set = "m"){
  
  # initializing key containers and values
  stratum_size =  100000 / n_strata
  strata_set = list() 
  strata_mixed_set = list()
  strata_outliers_set = list()
  stratum_index_replace_set = list()
  
  # Generate random stratified normal distributions
  for(i in 1:n_strata){
    strata_set[[paste0("stratum-",i)]] = rnorm(key_parameters[[i]][1], 
                                               key_parameters[[i]][2], 
                                               key_parameters[[i]][3])
  }
  
  # Generate outliers set from a t distribution shifted by the mean of the respective stratum
  for(i in 1:n_strata){
    stratum_size = key_parameters[[i]][1]
    stratum_outliers_count = inject_propotion * stratum_size
    stratum_mean = mean(strata_set[[paste0("stratum-",i)]])
    
    strata_outliers_set[[paste0("outlier_set-",i)]] = rt(stratum_outliers_count, t_df) + stratum_mean
    stratum_index_replace_set[[paste0("index_set", i)]] = sample(1:stratum_size, stratum_outliers_count)
  }
  
  # Inject outliers into the simulated stratum
  for(i in  1:n_strata){
    strata_mixed_set[[paste0("stratummixed-",i)]] = strata_set[[paste0("stratum-",i)]][-stratum_index_replace_set[[paste0("index_set", i)]]]
    strata_mixed_set[[paste0("stratummixed-",i)]] = c(strata_mixed_set[[paste0("stratummixed-",i)]], strata_outliers_set[[paste0("outlier_set-",i)]])
  }
  
  
  #  Sampling process
  
  if(sample_set == "m"){
    set_determinent = strata_mixed_set
  } else if(sample_set == "u") {
    set_determinent = strata_set
  }
  
  stratified_sample = c()
  for(i in 1:n_strata){
    stratum_sample_size = (key_parameters[[i]][1] / 100000) * sample_size
    stratified_sample = c(stratified_sample, sample(set_determinent[[i]], stratum_sample_size))
  }
  # The function returns  the stratified sample, the stratum set with and with out outliers
  return(list(stratified_sample, strata_set, strata_mixed_set))

}  
#__________________________ Estimators section _________________________________

# The Neyman Estimator
neyman_estimator = function(strata){
  strata_propotion_set = (sapply(strata, length)) / 100000
  strata_mean_set = sapply(strata, mean)
  neyman_estimate = sum(strata_propotion_set * strata_mean_set)
  
  return(neyman_estimate)
}

# The weighted mean estimator for each stratum
weighted_mean = function(strata_nooutliers, strata_outliers){
  strata_mean_set = sapply(strata_nooutliers, mean)
  strata_sd_set = sapply(strata_nooutliers, sd)
  
  weight_vec = lapply(seq_along(strata_outliers), function(i){
    weight_sub = 1 / (1 + (abs(strata_outliers[[i]] - strata_mean_set[names(strata_mean_set)[i]]) / strata_sd_set[names(strata_sd_set)[i]]))
    return(weight_sub)
  })
  
  w_mean = sapply(seq_along(weight_vec), function(i){
    return(sum(strata_outliers[[i]] * weight_vec[[i]]) / sum(weight_vec[[i]]))
  })
  
  return(w_mean)
}

# The trimmed mean  estimator for  each stratum
trim_mean = function(strata, trim_weight){
  trim_fun = function(x, trim_weight){
    trim_size = round(length(x) * trim_weight)
    trimmed_values = sort(x)[(trim_size + 1):(length(x) - trim_size)]
    return(trimmed_values)
  }
  
  t_strata_set = lapply(strata, trim_fun, trim_weight = trim_weight)
  t_mean = sapply(t_strata_set, mean)
  
  return(t_mean)
}


# The hybrid estimator capable of computing the Neyman,
# Wang Xu hybrid, and  proposed  hybrid estimators

hybrid_estimator = function(strata_nooutliers, strata_outliers, have_outliers = TRUE, trimmean = FALSE, trim_weight = 0.05){
  strata_propotion_set = (sapply(strata_nooutliers, length)) / 100000
  
  if(have_outliers & trimmean == FALSE){
    strata_weighted_mean_set = weighted_mean(strata_nooutliers, strata_outliers)
    hybrid_estimate = sum(strata_weighted_mean_set * strata_propotion_set)
  }
  else if(have_outliers & trimmean == TRUE){
    strata_trimmed_mean_set = trim_mean(strata_outliers, trim_weight = trim_weight)
    hybrid_estimate = sum(strata_trimmed_mean_set * strata_propotion_set)
  }
  else{
    hybrid_estimate = neyman_estimator(strata_nooutliers)
  }
  
  return(hybrid_estimate)
}


#_________________Running Part___________________________________________________

case_names = c("case-1-1", "case-1-2", "case-1-3", "case-1-4", "case-1-5", 
               "case-2-1", "case-2-2", "case-2-3", "case-2-4", "case-2-5", 
               "case-3-1", "case-3-2", "case-3-3", "case-3-4", "case-3-5", 
               "case-4-1", "case-4-2", "case-4-3", "case-4-4", "case-4-5", 
               "case-5-1", "case-5-2", "case-5-3", "case-5-4", "case-5-5", 
               "case-6-1", "case-6-2", "case-6-3", "case-6-4", "case-6-5")

propotion_option = c(0.05, 0.1)
dist_option = list(list(c(32145, 1, 2), c(28734, 1.5, 3), c(39121,2,4)),
                     list(c(18064, 5,3), c(25491,5,8), c(15678,8,2), c(22315, 6.3, 5), c(18452, 3,5)),
                     list(c(12341, 12, 4), c(15321, 5, 10), c(13456, 7,10), c(10765, 8,3), c(11984, 9,2), c(14213, 9,5), c(9572,4,7), c(12348,7,4)))

Neyman_estimates = c()
Wang_Xu_Hybrid_estimates =  c()
Proposed_Hybrid_estimates =  c()
summary_list_dt = list()
for (i in propotion_option) {
  Injection_propotion = i
  
  for (j in dist_option) {
    for(i in 1:5){
      Distribution_parameters_and_stratum_size = j
      number_of_strata = length(j)
      
      b = stratified_simulation(n_strata = number_of_strata,
                                key_parameters = Distribution_parameters_and_stratum_size,
                                inject_propotion = Injection_propotion)
      
      estimates = c(neyman_estimator(b[[3]]), hybrid_estimator(b[[2]], b[[3]]),  hybrid_estimator(b[[2]], b[[3]], trimmean = TRUE))
      Neyman_estimates = c(Neyman_estimates, estimates[1])
      Wang_Xu_Hybrid_estimates =  c(Wang_Xu_Hybrid_estimates, estimates[2])
      Proposed_Hybrid_estimates =  c(Proposed_Hybrid_estimates, estimates[3])
    }
    
  }
}
case_dt = data.frame(Neyman_estimates, Wang_Xu_Hybrid_estimates, Proposed_Hybrid_estimates, row.names = case_names)
library(knitr)
kable(case_dt, caption = "Estimated Parameters from Simulation", label = "Table 1")


```

After conducting the simulations, I computed the **Mean Squared Error (MSE), Variance, and Bias** for each estimator across all listed cases. The results are presented below, providing a comparative analysis of the estimators' performance under different conditions.

```{r echo=FALSE, warning=FALSE}
stratified_simulation = function(n_strata,
                                 key_parameters,
                                 inject_propotion = 0.1,
                                 t_df = 1,
                                 sample_size = 50000,
                                 sample_set = "m"){
  
  # initializing key containers and values
  strata_set = list() 
  strata_mixed_set = list()
  strata_outliers_set = list()
  stratum_index_replace_set = list()
  
  # Generate random stratified normal distributions
  for(i in 1:n_strata){
    strata_set[[paste0("stratum-",i)]] = rnorm(key_parameters[[i]][1], 
                                               key_parameters[[i]][2], 
                                               key_parameters[[i]][3])
  }
  
  # Generate outliers set from a t distribution shifted by the mean of the respective stratum
  for(i in 1:n_strata){
    stratum_size = key_parameters[[i]][1]
    stratum_outliers_count = inject_propotion * stratum_size
    stratum_mean = mean(strata_set[[paste0("stratum-",i)]])
    
    strata_outliers_set[[paste0("outlier_set-",i)]] = rt(stratum_outliers_count, t_df) + stratum_mean
    stratum_index_replace_set[[paste0("index_set", i)]] = sample(1:stratum_size, stratum_outliers_count)
  }
  
  # Inject outliers into the simulated stratum
  for(i in  1:n_strata){
    strata_mixed_set[[paste0("stratummixed-",i)]] = strata_set[[paste0("stratum-",i)]][-stratum_index_replace_set[[paste0("index_set", i)]]]
    strata_mixed_set[[paste0("stratummixed-",i)]] = c(strata_mixed_set[[paste0("stratummixed-",i)]], strata_outliers_set[[paste0("outlier_set-",i)]])
  }
  
  
  #  Sampling process
  
  if(sample_set == "m"){
    set_determinent = strata_mixed_set
  } else if(sample_set == "u") {
    set_determinent = strata_set
  }
  
  stratified_sample = c()
  for(i in 1:n_strata){
    stratum_sample_size = (key_parameters[[i]][1] / 100000) * sample_size
    stratified_sample = c(stratified_sample, sample(set_determinent[[i]], stratum_sample_size))
  }
  # The function returns  the stratified sample, the stratum set with and with out outliers
  return(list(stratified_sample, strata_set, strata_mixed_set))

}  
#__________________________ Estimators section _________________________________

# The Neyman Estimator
neyman_estimator = function(strata){
  strata_propotion_set = (sapply(strata, length)) / 100000
  strata_mean_set = sapply(strata, mean)
  neyman_estimate = sum(strata_propotion_set * strata_mean_set)
  
  return(neyman_estimate)
}

# The weighted mean estimator for each stratum
weighted_mean = function(strata_nooutliers, strata_outliers){
  strata_mean_set = sapply(strata_nooutliers, mean)
  strata_sd_set = sapply(strata_nooutliers, sd)
  
  weight_vec = lapply(seq_along(strata_outliers), function(i){
    weight_sub = 1 / (1 + (abs(strata_outliers[[i]] - strata_mean_set[names(strata_mean_set)[i]]) / strata_sd_set[names(strata_sd_set)[i]]))
    return(weight_sub)
  })
  
  w_mean = sapply(seq_along(weight_vec), function(i){
    sum(strata_outliers[[i]] * weight_vec[[i]]) / sum(weight_vec[[i]])
  })
  
  return(w_mean)
}

# The trimmed mean  estimator for  each stratum
trim_mean = function(strata, trim_weight){
  trim_fun = function(x, trim_weight){
    trim_size = round(length(x) * trim_weight)
    trimmed_values = sort(x)[(trim_size + 1):(length(x) - trim_size)]
    return(trimmed_values)
  }
  
  t_strata_set = lapply(strata, trim_fun, trim_weight = trim_weight)
  t_mean = sapply(t_strata_set, mean)
  
  return(t_mean)
}


# The hybrid estimator capable of deriving computing the Neyman,
# Wang Xu hybrid, and  proposed  hybrid estimators

hybrid_estimator = function(strata_nooutliers, strata_outliers, have_outliers = TRUE, trimmean = FALSE, trim_weight = 0.05){
  strata_propotion_set = (sapply(strata_nooutliers, length)) / 100000
  
  if(have_outliers & trimmean == FALSE){
    strata_weighted_mean_set = weighted_mean(strata_nooutliers, strata_outliers)
    hybrid_estimate = sum(strata_weighted_mean_set * strata_propotion_set)
  }
  else if(have_outliers & trimmean == TRUE){
    strata_trimmed_mean_set = trim_mean(strata_outliers, trim_weight = trim_weight)
    hybrid_estimate = sum(strata_trimmed_mean_set * strata_propotion_set)
  }
  else{
    hybrid_estimate = neyman_estimator(strata_nooutliers)
  }
  
  return(hybrid_estimate)
}


#_________________Running Part___________________________________________________

case_names = c("case-1-1", "case-1-2", "case-1-3", "case-1-4", "case-1-5", 
               "case-2-1", "case-2-2", "case-2-3", "case-2-4", "case-2-5", 
               "case-3-1", "case-3-2", "case-3-3", "case-3-4", "case-3-5", 
               "case-4-1", "case-4-2", "case-4-3", "case-4-4", "case-4-5", 
               "case-5-1", "case-5-2", "case-5-3", "case-5-4", "case-5-5", 
               "case-6-1", "case-6-2", "case-6-3", "case-6-4", "case-6-5")

propotion_option = c(0.05, 0.1)
dist_option = list(list(c(32145, 1, 2), c(28734, 1.5, 3), c(39121,2,4)),
                     list(c(18064, 5,3), c(25491,5,8), c(15678,8,2), c(22315, 6.3, 5), c(18452, 3,5)),
                     list(c(12341, 12, 4), c(15321, 5, 10), c(13456, 7,10), c(10765, 8,3), c(11984, 9,2), c(14213, 9,5), c(9572,4,7), c(12348,7,4)))

Neyman_estimates = c()
Wang_Xu_Hybrid_estimates =  c()
Proposed_Hybrid_estimates =  c()
summary_list_dt = list()
for (i in propotion_option) {
  Injection_propotion = i
  
  for (j in dist_option) {
    for(i in 1:100){
      Distribution_parameters_and_stratum_size = j
      number_of_strata = length(j)
      
      b = stratified_simulation(n_strata = number_of_strata,
                                key_parameters = Distribution_parameters_and_stratum_size,
                                inject_propotion = Injection_propotion)
      
      estimates = c(neyman_estimator(b[[3]]), hybrid_estimator(b[[2]], b[[3]]),  hybrid_estimator(b[[2]], b[[3]], trimmean = TRUE))
      Neyman_estimates = c(Neyman_estimates, estimates[1])
      Wang_Xu_Hybrid_estimates =  c(Wang_Xu_Hybrid_estimates, estimates[2])
      Proposed_Hybrid_estimates =  c(Proposed_Hybrid_estimates, estimates[3])
    }
    
  }
}
#__________MSE Varience and Bias computation___________________________

estimates_set = list(Neyman_estimates, Wang_Xu_Hybrid_estimates, Proposed_Hybrid_estimates)
var_set = c()
biased_set = c()
mu_set = c(1.53488, 5.391395,7.65506, 1.53488, 5.391395,7.65506)

for(i in estimates_set){
  ofset = 0
  for(j in 1:6){
    a = i[(1+ofset):(100 + ofset)]
    var_set = c(var_set,  var(a))
    biased_set = c(biased_set, (mean(a) - mu_set[j]))
    ofset = ofset + 100
  }
}
mse_set = var_set + (biased_set)**2


neyman_var_set = var_set[1:6]
neyman_biased_set = biased_set[1:6]
neyman_mse_set = mse_set[1:6]

wang_var_set = var_set[7:12]
wang_biased_set = biased_set[7:12]
wang_mse_set = mse_set[7:12]

proposed_var_set = var_set[13:18]
proposed_biased_set = biased_set[13:18]
proposed_mse_set = mse_set[13:18]

neyman_dt = rbind(round(neyman_var_set, 6), round(neyman_biased_set, 6), round(neyman_mse_set, 6))
colnames(neyman_dt) = c("Case-1", "Case-2", "Case-3", "Case-4", "Case-5", "Case-6")
rownames(neyman_dt) = c("Varience", "Biase", "MS Error")
library(knitr)
kable(neyman_dt, caption = "Neyman Estimator", label = "Table 2")

```

```{r echo=FALSE, warning=FALSE}

wang_dt = rbind(round(wang_var_set, 6), round(wang_biased_set, 6), round( wang_mse_set, 6))
colnames(wang_dt) = c("Case-1", "Case-2", "Case-3", "Case-4", "Case-5", "Case-6")
rownames(wang_dt) = c("Varience", "Biase", "MS Error")
library(knitr)
kable(wang_dt, caption = "Wang Xu Hybrid Estimator", label = "Table 2")

```

```{r  echo=FALSE, warning=FALSE}

proposed_dt = rbind(round(proposed_var_set, 6), round(proposed_biased_set, 6), round(proposed_mse_set, 6))
colnames(proposed_dt) = c("Case-1", "Case-2", "Case-3", "Case-4", "Case-5", "Case-6")
rownames(proposed_dt) = c("Varience", "Biase", "MS Error")
library(knitr)
kable(proposed_dt, caption = "Proposed Hybrid Estimator", label = "Table 2")

```

```{r echo=FALSE, warning=FALSE, message=FALSE}
Neyman_estimates = c()
Wang_Xu_Hybrid_estimates =  c()
Proposed_Hybrid_estimates =  c()
summary_list_dt = list()
for (i in propotion_option) {
  Injection_propotion = i
  
  for (j in dist_option) {
    for(i in c(1)){
      Distribution_parameters_and_stratum_size = j
      number_of_strata = length(j)
      
      b = stratified_simulation(n_strata = number_of_strata,
                                key_parameters = Distribution_parameters_and_stratum_size,
                                inject_propotion = Injection_propotion)
      
      estimates = c(neyman_estimator(b[[3]]), hybrid_estimator(b[[2]], b[[3]]),  hybrid_estimator(b[[2]], b[[3]], trimmean = TRUE))
      Neyman_estimates = c(Neyman_estimates, estimates[1])
      Wang_Xu_Hybrid_estimates =  c(Wang_Xu_Hybrid_estimates, estimates[2])
      Proposed_Hybrid_estimates =  c(Proposed_Hybrid_estimates, estimates[3])
      
      max_vec = c(sapply(b[[2]], max), sapply(b[[3]], max))
      min_vec = c(sapply(b[[2]], min), sapply(b[[3]], min))
      mean_vec = c(sapply(b[[2]], mean), sapply(b[[3]], mean))
      sd_vec = c(sapply(b[[2]], sd), sapply(b[[3]], sd))
      row_names = c(names(b[[2]]),names(b[[3]]))
      
      summary_dt = data.frame(max_vec, min_vec, mean_vec, sd_vec, row.names = row_names)
      colnames(summary_dt) =  c("Max_value", "Min_Value", "Mean", "SD")
      summary_list_dt = append(summary_list_dt, list(summary_dt))
    }
    
  }
}

unit_simulation_table =  rbind(Neyman_estimates, Wang_Xu_Hybrid_estimates, Proposed_Hybrid_estimates)
colnames(unit_simulation_table) = c("Case-1","Case-2","Case-3","Case-4","Case-5","Case-6")
library(knitr)
kable(unit_simulation_table, caption = "Estimated Parameters- one time Simulation", label = "Table 2")

```

The results indicate that the **Neyman estimator** is significantly affected by outliers, as evidenced by its extreme variance across different cases. In contrast, the **hybrid estimators** (including the **Proposed Hybrid Estimator** and the **Trimmed Hybrid Estimator**) demonstrate greater robustness to outliers. The lower variance and mean squared error (MSE) of these hybrid estimators suggest that they provide more stable and reliable estimates under the influence of outliers, making them preferable in scenarios where data contamination is a concern.\

```{r echo=FALSE, warning=FALSE, message=FALSE}
ylim_range <- range(c(neyman_mse_set[1:3], wang_mse_set[1:3], proposed_mse_set[1:3]))  
plot(c(3,5,8), neyman_mse_set[1:3], type = "l", col = "blue", ylim = ylim_range, 
     main = "5% outliers injection", xlab = "Stratum Size", ylab = "Mean Square Error", xaxt = "n")
lines.default(c(3,5,8), wang_mse_set[1:3], col = "brown")
lines.default(c(3,5,8), proposed_mse_set[1:3], col = "green")
axis(1, at = c(3,5,8), labels = c(3,5,8))
legend("topright", legend = c("Neyman MSE", "Wang MSE", "Proposed MSE"), 
       col = c("blue", "brown", "green"), lty = 1, cex = 0.8)

```

```{r echo=FALSE, warning=FALSE, message=FALSE}
ylim_range <- range(c(neyman_mse_set[4:6], wang_mse_set[4:6], proposed_mse_set[4:6]))  
plot(c(3,5,8), neyman_mse_set[4:6], type = "l", col = "blue", ylim = ylim_range, 
     main = "10% outliers injection", xlab = "Stratum Size", ylab = "Mean Square Error", xaxt = "n")
lines.default(c(3,5,8), wang_mse_set[1:3], col = "brown")
lines.default(c(3,5,8), proposed_mse_set[1:3], col = "green")
axis(1, at = c(3,5,8), labels = c(3,5,8))
legend("topright", legend = c("Neyman MSE", "Wang MSE", "Proposed MSE"), 
       col = c("blue", "brown", "green"), lty = 1, cex = 0.8)

```

\
**Code chunk:**

```{r echo=TRUE, warning=FALSE, eval=FALSE}
stratified_simulation = function(n_strata,
                                 key_parameters,
                                 inject_propotion = 0.1,
                                 t_df = 1,
                                 sample_size = 50000,
                                 sample_set = "m"){
  
  # initializing key containers and values
  strata_set = list() 
  strata_mixed_set = list()
  strata_outliers_set = list()
  stratum_index_replace_set = list()
  
  # Generate random stratified normal distributions
  for(i in 1:n_strata){
    strata_set[[paste0("stratum-",i)]] = rnorm(key_parameters[[i]][1], 
                                               key_parameters[[i]][2], 
                                               key_parameters[[i]][3])
  }
  
  # Generate outliers set from a t distribution shifted by the mean of the respective stratum
  for(i in 1:n_strata){
    stratum_size = key_parameters[[i]][1]
    stratum_outliers_count = inject_propotion * stratum_size
    stratum_mean = mean(strata_set[[paste0("stratum-",i)]])
    
    strata_outliers_set[[paste0("outlier_set-",i)]]
    = rt(stratum_outliers_count, t_df) + stratum_mean
    stratum_index_replace_set[[paste0("index_set", i)]] 
    = sample(1:stratum_size, stratum_outliers_count)
  }
  
  # Inject outliers into the simulated stratum
  for(i in  1:n_strata){
    strata_mixed_set[[paste0("stratummixed-",i)]] 
    = strata_set[[paste0("stratum-",i)]][-stratum_index_replace_set[[paste0("index_set", i)]]]
    strata_mixed_set[[paste0("stratummixed-",i)]]
    = c(strata_mixed_set[[paste0("stratummixed-",i)]], strata_outliers_set[[paste0("outlier_set-",i)]])
  }
  
  
  #  Sampling process
  
  if(sample_set == "m"){
    set_determinent = strata_mixed_set
  } else if(sample_set == "u") {
    set_determinent = strata_set
  }
  
  stratified_sample = c()
  for(i in 1:n_strata){
    stratum_sample_size = (key_parameters[[i]][1] / 100000) * sample_size
    stratified_sample = c(stratified_sample, sample(set_determinent[[i]], stratum_sample_size))
  }
  # The function returns  the stratified sample, the stratum set with and with out outliers
  return(list(stratified_sample, strata_set, strata_mixed_set))
  
}  
#__________________________ Estimators section _________________________________

# The Neyman Estimator
neyman_estimator = function(strata){
  strata_propotion_set = (sapply(strata, length)) / 100000
  strata_mean_set = sapply(strata, mean)
  neyman_estimate = sum(strata_propotion_set * strata_mean_set)
  
  return(neyman_estimate)
}

# The weighted mean estimator for each stratum
weighted_mean = function(strata_nooutliers, strata_outliers){
  strata_mean_set = sapply(strata_nooutliers, mean)
  strata_sd_set = sapply(strata_nooutliers, sd)
  
  weight_vec = lapply(seq_along(strata_outliers), function(i){
    weight_sub = 1 / (1 + (abs(strata_outliers[[i]] 
                               - strata_mean_set[names(strata_mean_set)[i]])
                           / strata_sd_set[names(strata_sd_set)[i]]))
    return(weight_sub)
  })
  
  w_mean = sapply(seq_along(weight_vec), function(i){
    return(sum(strata_outliers[[i]] * weight_vec[[i]]) / sum(weight_vec[[i]]))
  })
  
  return(w_mean)
}

# The trimmed mean  estimator for  each stratum
trim_mean = function(strata, trim_weight){
  trim_fun = function(x, trim_weight){
    trim_size = round(length(x) * trim_weight)
    trimmed_values = sort(x)[(trim_size + 1):(length(x) - trim_size)]
    return(trimmed_values)
  }
  
  t_strata_set = lapply(strata, trim_fun, trim_weight = trim_weight)
  t_mean = sapply(t_strata_set, mean)
  
  return(t_mean)
}


# The hybrid estimator capable of deriving computing the Neyman,
# Wang Xu hybrid, and  proposed  hybrid estimators

hybrid_estimator = function(strata_nooutliers, strata_outliers, have_outliers
                            = TRUE, trimmean = FALSE, trim_weight = 0.05){
  strata_propotion_set = (sapply(strata_nooutliers, length)) / 100000
  
  if(have_outliers & trimmean == FALSE){
    strata_weighted_mean_set = weighted_mean(strata_nooutliers, strata_outliers)
    hybrid_estimate = sum(strata_weighted_mean_set * strata_propotion_set)
  }
  else if(have_outliers & trimmean == TRUE){
    strata_trimmed_mean_set = trim_mean(strata_outliers, trim_weight = trim_weight)
    hybrid_estimate = sum(strata_trimmed_mean_set * strata_propotion_set)
  }
  else{
    hybrid_estimate = neyman_estimator(strata_nooutliers)
  }
  
  return(hybrid_estimate)
}


#_____________________________ simulation _____________________________________

case_names = c("case-1-1", "case-1-2", "case-1-3", "case-1-4", "case-1-5", 
               "case-2-1", "case-2-2", "case-2-3", "case-2-4", "case-2-5", 
               "case-3-1", "case-3-2", "case-3-3", "case-3-4", "case-3-5", 
               "case-4-1", "case-4-2", "case-4-3", "case-4-4", "case-4-5", 
               "case-5-1", "case-5-2", "case-5-3", "case-5-4", "case-5-5", 
               "case-6-1", "case-6-2", "case-6-3", "case-6-4", "case-6-5")

propotion_option = c(0.05, 0.1)
dist_option = list(list(c(32145, 1, 2), c(28734, 1.5, 3), c(39121,2,4)),
                   list(c(18064, 5,3), c(25491,5,8), c(15678,8,2), c(22315, 6.3, 5), c(18452, 3,5)),
                   list(c(12341, 12, 4), c(15321, 5, 10), c(13456, 7,10), c(10765, 8,3), 
                        c(11984, 9,2), c(14213, 9,5), c(9572,4,7), c(12348,7,4)))

Neyman_estimates = c()
Wang_Xu_Hybrid_estimates =  c()
Proposed_Hybrid_estimates =  c()
summary_list_dt = list()
for (i in propotion_option) {
  Injection_propotion = i
  
  for (j in dist_option) {
    for(i in 1:100){
      Distribution_parameters_and_stratum_size = j
      number_of_strata = length(j)
      
      b = stratified_simulation(n_strata = number_of_strata,
                                key_parameters = Distribution_parameters_and_stratum_size,
                                inject_propotion = Injection_propotion)
      
      estimates = c(neyman_estimator(b[[3]]), hybrid_estimator(b[[2]], b[[3]]),  
                    hybrid_estimator(b[[2]], b[[3]], trimmean = TRUE))
      Neyman_estimates = c(Neyman_estimates, estimates[1])
      Wang_Xu_Hybrid_estimates =  c(Wang_Xu_Hybrid_estimates, estimates[2])
      Proposed_Hybrid_estimates =  c(Proposed_Hybrid_estimates, estimates[3])
      
      max_vec = c(sapply(b[[2]], max), sapply(b[[3]], max))
      min_vec = c(sapply(b[[2]], min), sapply(b[[3]], min))
      mean_vec = c(sapply(b[[2]], mean), sapply(b[[3]], mean))
      sd_vec = c(sapply(b[[2]], sd), sapply(b[[3]], sd))
      row_names = c(names(b[[2]]),names(b[[3]]))
      
      summary_dt = data.frame(max_vec, min_vec, mean_vec, sd_vec, row.names = row_names)
      colnames(summary_dt) =  c("Max_value", "Min_Value", "Mean", "SD")
      summary_list_dt = append(summary_list_dt, list(summary_dt))
    }
    
  }
}


estimates_set = list(Neyman_estimates, Wang_Xu_Hybrid_estimates, Proposed_Hybrid_estimates)
var_set = c()
biased_set = c()
mu_set = c(1.53488, 5.391395,7.65506, 1.53488, 5.391395,7.65506)

for(i in estimates_set){
  ofset = 0
  for(j in 1:6){
    a = i[(1+ofset):(100 + ofset)]
    var_set = c(var_set,  mean((a-mean(a))**2))
    biased_set = c(biased_set, (mean(a) - mu_set[j]))
    ofset = ofset + 100
  }
}
mse_set = var_set + (biased_set)**2


neyman_var_set = var_set[1:6]
neyman_biased_set = biased_set[1:6]
neyman_mse_set = mse_set[1:6]

wang_var_set = var_set[7:12]
wang_biased_set = biased_set[7:12]
wang_mse_set = mse_set[7:12]

proposed_var_set = var_set[13:18]
proposed_biased_set = biased_set[13:18]
proposed_mse_set = mse_set[13:18]

neyman_dt = rbind(neyman_var_set, neyman_biased_set, neyman_mse_set)
colnames(neyman_dt) = c("Case-1", "Case-2", "Case-3", "Case-4", "Case-5", "Case-6")
rownames(neyman_dt) = c("Varience", "Biase", "MS Error")
neyman_dt

round(var_set, 6)
round(biased_set, 6)
round(mse_set, 6)

print(neyman_mse_set)
print(wang_mse_set)
print(proposed_mse_set)


for(i in 1:6){
  value = c(value, neyman_mse_set[i])
  value = c(value, wang_mse_set[i])
  value = c(value, proposed_mse_set[i])
}


# __________________________________________Graphing ________________
library(ggplot2)
library(dplyr)


data <- data.frame(
  Category = rep(c("Case_1", "Case_2", "Case_3", "Case_4", "Case_5", "Case_6"), each = 3),
  Subcategory = rep(c("Neyman", "Wang", "Proposed"), times = 6),
  Value = value
)


data <- data %>%
  group_by(Category) %>%
  mutate(Percentage = Value / sum(Value) * 100)
data

ggplot(data, aes(x = "", y = Percentage, fill = Subcategory)) +
  geom_bar(stat = "identity", width = 1, color = "white") +
  coord_polar(theta = "y") + 
  facet_wrap(~ Category) +  
  scale_fill_manual(values = c("#1b9e77", "#d95f02", "#7570b3")) +
  labs(
    title = "Comparison of Estimators Across Cases",
    fill = "Estimator"
  ) +
  theme_void() +  
  theme(
    plot.title = element_text(hjust = 0.5, face = "bold"),
    legend.position = "bottom"
  )

```
